NumPy---Array Programming in Python

### 2020-02-14 body.tex
Edit summary

NumPy operates on in-memory arrays using the CPU. To utilize modern,
specialized storage and hardware, there has been a recent
proliferation of Python array packages. Unlike with the Numarray and
Numeric divide, it is now much harder for these new libraries to
fracture the user community---given how much work already builds
on-top of NumPy.  However, to provide the ecosystem with access to
new and exploratory technologies, NumPy is transitioning into a
central coordinating mechanism that specifies a well-defined array
programming API and
dispatches it, as appropriate, to specialized array implementations.

>>>>

NumPy operates on in-memory arrays using the CPU. To utilize modern,
specialized storage and hardware, there has been a recent
proliferation of Python array packages. Unlike with the Numarray and
Numeric divide, it is now much harder for these new libraries to
fracture the user community---given how much work already builds
on top of NumPy.  However, to provide the ecosystem with access to
new and exploratory technologies, NumPy is transitioning into a
central coordinating mechanism that specifies a well-defined array
programming API and
dispatches it, as appropriate, to specialized array implementations.
